Income Disparity and Its Influence on Higher Education Affordability and Access

### 2024-02-12 starter_folder-main 4/paper/paper.qmd
updated title and authors

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Income Disparity and Its Influence on Higher Education Affordability and Access"
author: 
  - Michael Fang
  - Harrison Huang
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
